Observed vs. Simulated Year Comparison

### 2023-03-10 03-post-process/output-plots-children/05-length-based-values.Rmd
Add year labels to scatter plots in output-plots

  # realized pairs
  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

}

@@

  # realized pairs
  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
```

@@

  # realized pairs
  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

@@

  # realized pairs
  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

>>>>

  # realized pairs
  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(L_Pb_mean ~ E_scaled_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

@@

  # realized pairs
  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr\\,\\rightarrow\\, Spring\\,Smolt\\,Growth\\, Factor$"))
```

@@

  # realized pairs
  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

@@

  # realized pairs
  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Mb_Ma_mean ~ L_Mb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}
